%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{James}{DeFilippo}{ 
\href{mailto:jms.defilippo@gmail.com}{jms.defilippo@gmail.com} | 978.227.8300 | \href{https://jdefilippo.github.io/}{jdefilippo.github.io} \\
18 Cuba Street, Watertown, MA 02472 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UMass Lowell}
\descript{B.S. in Mathematics}
\location{Magna Cum Laude}
\location{2011 - 2015 | GPA: 3.73}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\textbullet{} Python 
\textbullet{} C
\textbullet{} C++ \\
\textbullet{} MatLab 
\textbullet{} Simulink \\
\textbullet{} BASH  
\textbullet{} Assembly 
\sectionsep

\subsection{Technologies}
\textbullet{} Linux 
\textbullet{} MySQL \\
\textbullet{} MagicDraw  
\textbullet{} UML \\ 
\textbullet{} Git 
\textbullet{} SVN \\
\textbullet{} Simics 
\textbullet{} VxWorks \\ 
\textbullet{} HTML
\textbullet{} CSS
\sectionsep

\subsection{Domain Knowledge}
\textbullet{} Software Architecture \\ 
\textbullet{} Spiral Development \\  
\textbullet{} Space Systems \\ 
\textbullet{} Embedded Systems \\ 
\textbullet{} Fault Tolerance \\ 
\textbullet{} Kalman Filtering \\ 
\textbullet{} Applied Probability 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\textbullet{} Mathematical Modeling \\
\textbullet{} Measure and Probability Theory \\
\textbullet{} Stochastic Processes \\ 
\textbullet{} Partial Differential Equations \\
\textbullet{} Abstract Algebra \\ 
\textbullet{} Introduction to Algorithms \\
\textbullet{} Foundations of Computer Science \\
\textbullet{} Computer Organization and Assembly Language Programming \\
\textbullet{} Computing I-III \\
\textbullet{} Probability and Statistics \\
\textbullet{} Introduction to Topology \\ 
\textbullet{} Number Theory \\
\textbullet{} Real Analysis
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     DISTINCTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Distinctions}
\textbullet{} Commonwealth Scholarship \\ 
\textbullet{} Zamankos Endowed Scholarship  \\
\textbullet{} Pi Mu Epsilon \\ 
\textbullet{} Dean's List \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Draper}
\descript{| Software Engineer }
\location{May 2015 - Present | Cambridge, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed, developed, and tested key components of fault-tolerant flight software in embedded C for NASA-funded reusable spacecraft.  
\item Generated simulation and modeling software in MATLAB and Simulink to analyze flight trajectories using Kalman filtering algorithms. 
\item Wrote object-oriented modernization design proposal for a major department’s analysis tools to generalize and expand the functionality of existing software.  
\item Received Outstanding Contribution Award and subsequent promotion based on performance reviews.
\item Designed Python framework for auto-testing legacy software. 
\end{tightemize}
\sectionsep

\vspace{\topsep} 
\vspace{\topsep} 

\runsubsection{IBM}
\descript{| Software Co-op }
\location{June 2014 - August 2014 | Littleton, MA}
\begin{tightemize}
\item Designed C++ test cases to ensure full code coverage. 
\item Learned company’s software lifecycle for Lotus Notes, working to resolve outstanding PRs and implemented test cases using Visual Studio IDE and within a Windows environment.
\end{tightemize}
\sectionsep

\vspace{\topsep} 
\vspace{\topsep} 

\runsubsection{Putnam Investments}
\descript{| Software Co-op }
\location{ January 2014 - May 2014 | Andover, MA}
\begin{tightemize}
\item Designed and implemented Python software to automatically update SQL tables with daily changes to employee information. 
\item Led efforts to create a department-wide version control using GIT. 
\end{tightemize}
\sectionsep

\vspace{\topsep} 
\vspace{\topsep} 

\runsubsection{Engaging Computing Group}
\descript{| Undergrad Researcher }
\location{ May 2012 - December 2013 | Lowell, MA}
\begin{tightemize} 
\item Developed prototype evaluation system in Python to automatically grade submissions in a freshman-level CS course.
\item Designed grading rubrics and teaching materials for an introductory Mobile Computing class.
\item Contributed to the App Inventor Gallery, a code-sharing platform for community created Android apps, using JavaScript and Qooxdoo, an Ajax web-application framework. 
\end{tightemize}
\sectionsep

\vspace{\topsep} 
\vspace{\topsep} 

\runsubsection{Mathematics Department}
\descript{| Undergrad Researcher }
\location{ September 2012 - December 2013 | Lowell, MA}
\begin{tightemize}
\item Worked with a team of undergraduate and graduate students under Professor James Propp on problems involving de-randomized rotor-router models of stochastic processes.
\item Communicated ﬁndings through technical writing and computer simulations.
\item Presented results at the 2013 Mid-Hudson Mathematics Conference.
\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}